### 2025-04-15 reports/paper/resources/intervention-density-witnin-combos-a.tex
some revisions

% Created by tikzDevice version 0.12.3.1 on 2023-08-04 14:49:59
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 38.22, 31.50) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 38.22, 31.50) rectangle (246.94,165.68);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[fill=fillColor] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[fill=fillColor] ( 62.31, 37.60) rectangle ( 69.61, 37.60);

\path[fill=fillColor] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[fill=fillColor] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

\path[fill=fillColor] ( 84.20, 37.60) rectangle ( 91.50, 37.60);

\path[fill=fillColor] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[fill=fillColor] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[fill=fillColor] (106.10, 37.60) rectangle (113.39, 37.60);

\path[fill=fillColor] (113.39, 37.60) rectangle (120.69,159.58);

\path[fill=fillColor] (120.69, 37.60) rectangle (127.99, 37.60);

\path[fill=fillColor] (127.99, 37.60) rectangle (135.29, 37.60);

\path[fill=fillColor] (135.29, 37.60) rectangle (142.58, 37.60);

\path[fill=fillColor] (142.58, 37.60) rectangle (149.88, 37.60);

\path[fill=fillColor] (149.88, 37.60) rectangle (157.18, 37.60);

\path[fill=fillColor] (157.18, 37.60) rectangle (164.48, 37.60);

\path[fill=fillColor] (164.48, 37.60) rectangle (171.78, 37.60);

\path[fill=fillColor] (171.78, 37.60) rectangle (179.07, 37.60);

\path[fill=fillColor] (179.07, 37.60) rectangle (186.37, 37.60);

\path[fill=fillColor] (186.37, 37.60) rectangle (193.67, 37.60);

\path[fill=fillColor] (193.67, 37.60) rectangle (200.97, 37.60);

\path[fill=fillColor] (200.97, 37.60) rectangle (208.27, 37.60);

\path[fill=fillColor] (208.27, 37.60) rectangle (215.56, 37.60);

\path[fill=fillColor] (215.56, 37.60) rectangle (222.86, 37.60);

\path[fill=fillColor] (222.86, 37.60) rectangle (230.16, 37.60);

\path[fill=fillColor] (230.16, 37.60) rectangle (237.46, 37.60);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] ( 47.71, 37.60) rectangle ( 55.01,110.79);

\path[draw=drawColor,line width= 0.4pt] ( 55.01, 37.60) rectangle ( 62.31, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 62.31, 37.60) rectangle ( 69.61, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 69.61, 37.60) rectangle ( 76.90, 62.00);

\path[draw=drawColor,line width= 0.4pt] ( 76.90, 37.60) rectangle ( 84.20, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 84.20, 37.60) rectangle ( 91.50, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 91.50, 37.60) rectangle ( 98.80, 37.60);

\path[draw=drawColor,line width= 0.4pt] ( 98.80, 37.60) rectangle (106.10, 37.60);

\path[draw=drawColor,line width= 0.4pt] (106.10, 37.60) rectangle (113.39, 37.60);

\path[draw=drawColor,line width= 0.4pt] (113.39, 37.60) rectangle (120.69, 62.00);

\path[draw=drawColor,line width= 0.4pt] (120.69, 37.60) rectangle (127.99, 37.60);

\path[draw=drawColor,line width= 0.4pt] (127.99, 37.60) rectangle (135.29, 62.00);

\path[draw=drawColor,line width= 0.4pt] (135.29, 37.60) rectangle (142.58, 37.60);

\path[draw=drawColor,line width= 0.4pt] (142.58, 37.60) rectangle (149.88, 62.00);

\path[draw=drawColor,line width= 0.4pt] (149.88, 37.60) rectangle (157.18, 37.60);

\path[draw=drawColor,line width= 0.4pt] (157.18, 37.60) rectangle (164.48, 37.60);

\path[draw=drawColor,line width= 0.4pt] (164.48, 37.60) rectangle (171.78, 37.60);

\path[draw=drawColor,line width= 0.4pt] (171.78, 37.60) rectangle (179.07, 37.60);

\path[draw=drawColor,line width= 0.4pt] (179.07, 37.60) rectangle (186.37, 37.60);

\path[draw=drawColor,line width= 0.4pt] (186.37, 37.60) rectangle (193.67, 62.00);

\path[draw=drawColor,line width= 0.4pt] (193.67, 37.60) rectangle (200.97, 37.60);

\path[draw=drawColor,line width= 0.4pt] (200.97, 37.60) rectangle (208.27, 37.60);

\path[draw=drawColor,line width= 0.4pt] (208.27, 37.60) rectangle (215.56, 37.60);

\path[draw=drawColor,line width= 0.4pt] (215.56, 37.60) rectangle (222.86, 37.60);

\path[draw=drawColor,line width= 0.4pt] (222.86, 37.60) rectangle (230.16, 62.00);

\path[draw=drawColor,line width= 0.4pt] (230.16, 37.60) rectangle (237.46, 37.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (120.69, 31.50) -- (120.69,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 38.22, 31.50) rectangle (246.94,165.68);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 34.85) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 62.29) {5};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27, 89.74) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,117.18) {15};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 33.27,144.62) {20};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 37.60) --
	( 38.22, 37.60);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 65.05) --
	( 38.22, 65.05);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47, 92.49) --
	( 38.22, 92.49);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,119.93) --
	( 38.22,119.93);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.47,147.38) --
	( 38.22,147.38);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 47.71, 28.75) --
	( 47.71, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.10, 28.75) --
	(106.10, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.48, 28.75) --
	(164.48, 31.50);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.86, 28.75) --
	(222.86, 31.50);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 47.71, 21.04) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.10, 21.04) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.48, 21.04) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.86, 21.04) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (142.58,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.59) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,143.84) rectangle (244.95,163.87);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,157.35) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,146.34) rectangle (176.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (172.95,146.34) -- (172.95,154.34);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,147.59) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,113.81) rectangle (240.85,141.84);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (168.95,135.32) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (168.95,124.31) rectangle (176.95,132.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (168.95,116.31) rectangle (176.95,124.31);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (169.45,116.81) rectangle (176.45,123.81);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,125.55) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (178.95,117.55) {Observed};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (  2.22,170.34) {a)};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-04-14 23:48:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage{upgreek}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (252.94,180.68);
\end{scope}
\begin{scope}
\path[clip] ( 39.16, 31.76) rectangle (246.94,165.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] ( 39.16, 31.76) rectangle (246.95,165.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] ( 48.60, 37.85) rectangle ( 55.87, 37.85);

\path[fill=fillColor] ( 55.87, 37.85) rectangle ( 63.13, 47.21);

\path[fill=fillColor] ( 63.13, 37.85) rectangle ( 70.40, 37.85);

\path[fill=fillColor] ( 70.40, 37.85) rectangle ( 77.66, 47.21);

\path[fill=fillColor] ( 77.66, 37.85) rectangle ( 84.93, 47.21);

\path[fill=fillColor] ( 84.93, 37.85) rectangle ( 92.19, 37.85);

\path[fill=fillColor] ( 92.19, 37.85) rectangle ( 99.46, 47.21);

\path[fill=fillColor] ( 99.46, 37.85) rectangle (106.72,159.59);

\path[fill=fillColor] (106.72, 37.85) rectangle (113.99, 37.85);

\path[fill=fillColor] (113.99, 37.85) rectangle (121.26, 37.85);

\path[fill=fillColor] (121.26, 37.85) rectangle (128.52, 37.85);

\path[fill=fillColor] (128.52, 37.85) rectangle (135.79, 37.85);

\path[fill=fillColor] (135.79, 37.85) rectangle (143.05, 37.85);

\path[fill=fillColor] (143.05, 37.85) rectangle (150.32, 37.85);

\path[fill=fillColor] (150.32, 37.85) rectangle (157.58, 37.85);

\path[fill=fillColor] (157.58, 37.85) rectangle (164.85, 37.85);

\path[fill=fillColor] (164.85, 37.85) rectangle (172.11, 37.85);

\path[fill=fillColor] (172.11, 37.85) rectangle (179.38, 37.85);

\path[fill=fillColor] (179.38, 37.85) rectangle (186.64, 37.85);

\path[fill=fillColor] (186.64, 37.85) rectangle (193.91, 37.85);

\path[fill=fillColor] (193.91, 37.85) rectangle (201.17, 37.85);

\path[fill=fillColor] (201.17, 37.85) rectangle (208.44, 37.85);

\path[fill=fillColor] (208.44, 37.85) rectangle (215.70, 37.85);

\path[fill=fillColor] (215.70, 37.85) rectangle (222.97, 37.85);

\path[fill=fillColor] (222.97, 37.85) rectangle (230.23, 37.85);

\path[fill=fillColor] (230.23, 37.85) rectangle (237.50, 37.85);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] ( 48.60, 37.85) rectangle ( 55.87, 37.85);

\path[draw=drawColor,line width= 0.4pt] ( 55.87, 37.85) rectangle ( 63.13, 47.21);

\path[draw=drawColor,line width= 0.4pt] ( 63.13, 37.85) rectangle ( 70.40, 37.85);

\path[draw=drawColor,line width= 0.4pt] ( 70.40, 37.85) rectangle ( 77.66, 47.21);

\path[draw=drawColor,line width= 0.4pt] ( 77.66, 37.85) rectangle ( 84.93, 47.21);

\path[draw=drawColor,line width= 0.4pt] ( 84.93, 37.85) rectangle ( 92.19, 37.85);

\path[draw=drawColor,line width= 0.4pt] ( 92.19, 37.85) rectangle ( 99.46, 47.21);

\path[draw=drawColor,line width= 0.4pt] ( 99.46, 37.85) rectangle (106.72, 47.21);

\path[draw=drawColor,line width= 0.4pt] (106.72, 37.85) rectangle (113.99, 37.85);

\path[draw=drawColor,line width= 0.4pt] (113.99, 37.85) rectangle (121.26, 37.85);

\path[draw=drawColor,line width= 0.4pt] (121.26, 37.85) rectangle (128.52, 37.85);

\path[draw=drawColor,line width= 0.4pt] (128.52, 37.85) rectangle (135.79, 47.21);

\path[draw=drawColor,line width= 0.4pt] (135.79, 37.85) rectangle (143.05, 37.85);

\path[draw=drawColor,line width= 0.4pt] (143.05, 37.85) rectangle (150.32, 37.85);

\path[draw=drawColor,line width= 0.4pt] (150.32, 37.85) rectangle (157.58, 94.04);

\path[draw=drawColor,line width= 0.4pt] (157.58, 37.85) rectangle (164.85, 37.85);

\path[draw=drawColor,line width= 0.4pt] (164.85, 37.85) rectangle (172.11, 47.21);

\path[draw=drawColor,line width= 0.4pt] (172.11, 37.85) rectangle (179.38, 37.85);

\path[draw=drawColor,line width= 0.4pt] (179.38, 37.85) rectangle (186.64, 37.85);

\path[draw=drawColor,line width= 0.4pt] (186.64, 37.85) rectangle (193.91, 47.21);

\path[draw=drawColor,line width= 0.4pt] (193.91, 37.85) rectangle (201.17, 37.85);

\path[draw=drawColor,line width= 0.4pt] (201.17, 37.85) rectangle (208.44, 56.58);

\path[draw=drawColor,line width= 0.4pt] (208.44, 37.85) rectangle (215.70, 37.85);

\path[draw=drawColor,line width= 0.4pt] (215.70, 37.85) rectangle (222.97, 37.85);

\path[draw=drawColor,line width= 0.4pt] (222.97, 37.85) rectangle (230.23, 47.21);

\path[draw=drawColor,line width= 0.4pt] (230.23, 37.85) rectangle (237.50, 37.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (121.26, 31.76) -- (121.26,165.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 39.16, 31.76) rectangle (246.95,165.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 35.09) {0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21, 74.89) {10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,114.69) {20};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 34.21,154.49) {30};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 37.85) --
	( 39.16, 37.85);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41, 77.65) --
	( 39.16, 77.65);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,117.45) --
	( 39.16,117.45);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 36.41,157.25) --
	( 39.16,157.25);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 48.60, 29.01) --
	( 48.60, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] (106.72, 29.01) --
	(106.72, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] (164.85, 29.01) --
	(164.85, 31.76);

\path[draw=drawColor,line width= 0.4pt,line join=round] (222.97, 29.01) --
	(222.97, 31.76);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 48.60, 21.30) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (106.72, 21.30) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (164.85, 21.30) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (222.97, 21.30) {0.6};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (143.05,  7.77) {Exposure to soluble MWF (mg/m$^3$)};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 17.51, 98.72) {Density};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.95,144.14) rectangle (246.94,167.67);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (170.95,161.15) {Target exposure limit:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.95,146.64) rectangle (178.95,154.64);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 7pt off 3pt ,line join=round] (174.95,146.64) -- (174.95,154.64);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,147.89) {0.25 mg/m$^3$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.95,110.11) rectangle (246.35,141.64);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (170.95,135.12) {Distribution:};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.95,120.61) rectangle (178.95,128.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{211,211,211}

\path[fill=fillColor] (170.95,120.61) rectangle (178.95,128.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{fillColor}{RGB}{255,255,255}

\path[fill=fillColor] (170.95,112.61) rectangle (178.95,120.61);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt] (171.45,113.11) rectangle (178.45,120.11);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,121.85) {Post-intervention};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (252.94,180.67);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (184.45,113.85) {Observed};
\end{scope}
\end{tikzpicture}
